Native advertising as a content marketing strategy

### 2024-09-10 analysis/paper/paper.Rmd
weiter

<details>
<summary>Click to expand the code chunk</summary>

@@

@@

<details>
<summary>Click to expand the code chunk</summary>

@@

# Results and Discussion

@@

<details>
<summary>Click to expand the code chunk</summary>
```{r warning=FALSE, message=FALSE,error=FALSE, echo=FALSE, results='hide'}

@@

```{r echo=F, eval=T, message=F , warning= FALSE}
IND_kable
```

### summarizes the total reach per portal, provides descriptive statistics for reach, and creates a histogram of reach values (filtered to be between 0 and 30,000)

```{r echo=F, eval=T, message=F , warning= FALSE}
# Portals by reach
reach <- dta %>%
  group_by(FROM) %>%
  summarise(reach = sum(REACH)) %>%
  arrange(desc(reach))

@@

### summary statistics for reach (mean, median, min, max, total). It then connects these statistics with the corresponding clickbait descriptions

@@

# Create the clickbait DataFrame
clickbait <- data.frame(
  number = c(1, 2, 3, 4, 5, 6, 7),
  text = c("Nedefinirane zamjenice", "Neizvjesnost", "Stil obrnutog narativa",
           "Naglašavanje emocija", "Korištenje brojkama", "Više kombinacija",
           "Nije clickbait naslov")
)

@@

# Display the result
result %>%
  select(text, count, mean_reach, median_reach, min_reach, max_reach, total_reach) %>%
  kable(format = "html", 
        col.names = c("Clickbait Type", "Count", "Mean Reach", "Median Reach", 
                      "Min Reach", "Max Reach", "Total Reach"),
        caption = "Summary Statistics by Clickbait Type") %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed"), 
                full_width = F, position = "left")

@@

### calculates summary statistics for reach, and then merges these results with the descriptions of each source type

```{r echo=F, eval=T, message=F , warning= FALSE}
# Create the 'izvori' DataFrame
izvori <- data.frame(
  number = c(1, 2, 3, 4, 5, 6, 7),
  text = c(
    "Nema izvora / izjave",
    "Izvor iz organizacije / tvrtke",
    "Brend ambasador",
    "Influencer, celebrity, slavna / poznata osoba",
    "Korisnik proizvoda ili usluge (poduzetnik, Marica iz Benkovca)",
    "Više izvora",
    "Izvor nepovezan s proizvodom ili uslugom koja se promovira"
  )
)

@@

# Display the result
result %>%
  select(text, count, mean_reach, median_reach, min_reach, max_reach, total_reach) %>%
  kable(format = "html", 
        col.names = c("Source Type", "Count", "Mean Reach", "Median Reach", 
                      "Min Reach", "Max Reach", "Total Reach"),
        caption = "Summary Statistics by Source Type") %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed"), 
                full_width = F, position = "left")

@@

The advertiser's logo, or elements of the advertiser's visual identity, were included in the visual content of the analysed native ads in 34.44% of cases, while in 356 out of 543 analysed articles, this was not the case, meaning they did not contain a visual link to the advertiser.
Regarding the content characteristics of native ads in this study, the types of sources or statements in the articles were also observed, as shown in Table 3. The ratio of ads using sources to those that do not is approximately similar, with the most common sources in the ads being individuals from the organization, i.e., the advertiser (19.71%). The second most common sources, with a prevalence of 10.31%, were those not directly connected to the product or service, while multiple sources were present in 7.55% of the ads, and in 6.81% of the ads, there was testimony or a statement from a person presented as a direct user of the product or service. Celebrities were also used as sources in native ads, with brand ambassadors’ statements used in 4.79% of cases, and influencers or celebrities were present in 3.5% of the analysed ads.

### correlation between different clickbait types across industries/correlation matrix to examine relationships between clickbait usage in various industries.

@@

### correlation between different source types across industries/correlation matrix to explore how different source types are used together within various industrie

@@

@@

### how different clickbait types are distributed across various industries

# Step 3: Create a Table Showing Distribution
# You can simply view the table
# industry_clickbait %>%
#   select(category, text, Count, Percent) %>%
#   kable(format = "html", 
#         col.names = c("Industry", "Clickbait Type", "Count", "Percentage"),
#         caption = "Distribution of Clickbait Types Across Industries") %>%
#   kable_styling(bootstrap_options = c("striped", "hover", "condensed"), 
#                 full_width = F, position = "left")
# Optional Step: Create a Heatmap for Visualization
ggplot(industry_clickbait, aes(x = category, y = text, fill = Percent)) +
  geom_tile() +
  scale_fill_gradient(low = "white", high = "blue") +
  labs(title = "Distribution of Clickbait Types Across Industries",
       x = "Industry",
       y = "Clickbait Type",
       fill = "Percentage") +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))
```

### how different source types are distributed across various industries

@@

# Assuming 'dta' is your data frame with 'INDUSTRIJA' and 'IZVORI...IZJAVE' columns

@@

<!-- <details> -->
<!-- <summary>Click to expand the code chunk</summary> -->

# Create the clickbait DataFrame
clickbait <- data.frame(
  number = c(1, 2, 3, 4, 5, 6, 7),
  text = c("Nedefinirane zamjenice", "Neizvjesnost", "Stil obrnutog narativa",
           "Naglašavanje emocija", "Korištenje brojkama", "Više kombinacija",
           "Nije clickbait naslov")
)

# Grouping, summarizing, and calculating percentages
result <- dta %>%
  group_by(CLICKBAIT) %>%
  summarise(N = n()) %>%
  mutate(percent = round(N / sum(N) * 100, 2)) %>%
  arrange(desc(N)) %>%
  left_join(clickbait, by = c("CLICKBAIT" = "number"))

# Create a beautiful table
result %>%
  select(text, N, percent) %>%
  kable("html", col.names = c("Description", "Count", "%")) %>%
  add_header_above(c("Table 1. Prevalence of clickbait headline characteristics in the analyzed native ads" = 3)) %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive"), 
                full_width = FALSE, position = "left") %>%
  column_spec(1, width = "20em") %>%
  column_spec(2, width = "10em") %>%
  column_spec(3, width = "10em")

```
<!-- </details> -->

In the vast majority of the analyzed native ads (94.48%), the advertiser's brand name was not mentioned in the headline, while in 5.52%, or thirty out of the 543 articles, the brand name was included in the headline. Here, we will add the distinction between a sponsored article, which typically mentions the advertiser in the headline, and native advertising, which generally does not, as it employs a subtler advertising tactic.

The majority of the headlines, 71.09%, were declarative sentences, while one-fifth (20.26%) were interrogative, and 8.95% were exclamatory sentences. Regarding the content characteristics of the observed native ads, it is noteworthy that all analyzed ads included visual elements, with photography being the most prominent, either alone or in combination with other types of visual content. As shown in Table 2, in 73.67% of cases, the ads were equipped exclusively with photographic content, while in 11.97% of cases, the ads included both photographic and graphic content. In 11.05% of ads, photographic content was accompanied by video content, and in 2.39% of cases, the native ads contained a combination of photo, video, and graphic content.

<!-- <details> -->
<!-- <summary>Click to expand the code chunk</summary> -->

# Create the 'oprema' DataFrame
oprema <- data.frame(
  number = c(1, 2, 3, 4, 5, 6, 7, 8),
  text = c(
    "Foto-sadržaj",
    "Video-sadržaj",
    "Grafika ili infografika (ne uključuje logo)",
    "Foto i video sadržaj",
    "Foto i grafički sadržaj",
    "Video i grafički sadržaj",
    "Foto, video i grafički sadržaj",
    "Članak nema nikakvu opremu"
  )
)

```
<!-- </details> -->

The advertiser's logo, or elements of the advertiser's visual identity, were featured as part of the visual content in 34.44% of the analyzed native ads. However, in 356 out of the 543 analyzed articles, this was not the case, meaning they did not contain a visual link to the advertiser.

Among the content characteristics of native ads in this study, the types of sources or statements within the articles were also examined, as shown in Table 3. The ratio of ads that use sources to those that do not is approximately similar. Among the ads that include a source, the most common type is a person from the organization or the advertiser (19.71%). The second most prominent, with 10.31% representation, are sources not directly connected to the product or service, while in 7.55% of cases, multiple sources were present. In 6.81% of ads, the source was a testimony or statement from someone presented as a direct user of the product or service. Well-known individuals are also used as sources in native ads; brand ambassadors were used in 4.79% of cases, while influencers or celebrities were featured in 3.5% of the observed ads.

<!-- <details> -->
<!-- <summary>Click to expand the code chunk</summary> -->

# Create the 'izvori' DataFrame
izvori <- data.frame(
  number = c(1, 2, 3, 4, 5, 6, 7),
  text = c(
    "Nema izvora / izjave",
    "Izvor iz organizacije / tvrtke",
    "Brend ambasador",
    "Influencer, celebrity, slavna / poznata osoba",
    "Korisnik proizvoda ili usluge (poduzetnik, Marica iz Benkovca)",
    "Više izvora",
    "Izvor nepovezan s proizvodom ili uslugom koja se promovira"
  )
)

# Grouping, summarizing, and calculating percentages
result <- dta %>%
  group_by(`IZVORI...IZJAVE`) %>%
  summarise(N = n()) %>%
  mutate(percent = round(N / sum(N) * 100, 2)) %>%
  arrange(desc(N)) %>%
  left_join(izvori, by = c("IZVORI...IZJAVE" = "number"))

# Create a beautiful table
result %>%
  select(text, N, percent) %>%
  kable("html", col.names = c("Description", "Count", "%")) %>%
  add_header_above(c("Table 3. Representation of different types of sources in the statements" = 3)) %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive"), 
                full_width = FALSE, position = "left") %>%
  column_spec(1, width = "30em") %>%
  column_spec(2, width = "10em") %>%
  column_spec(3, width = "10em")

```
<!-- </details> -->

The conclusion of the research can be summarized through several key points. An analysis of 543 native ads published on six Croatian internet portals showed a significant presence of clickbait titles, where almost 80% of the titles had at least one clickbait characteristic, with the suspense style being most often used. Although a smaller part of the headlines (5.52%) mentioned the brand, most of them were neutral about direct advertising. Titles are mostly declarative sentences, while visual elements, especially photos, were present in all ads, with the advertiser's logo included in 34.44% of cases. In the area of ​​sources of statements, almost half of the articles did not use statements, while in other articles the sources were most often people from the organization, with a relatively small presence of influencers and celebrities. These findings indicate the dominance of clickbait titles and the significant role of visual equipment in native advertising, while direct association with the brand and the use of authoritative sources are less common.

>>>>

@@

<details>
<summary>Import libraries/click to see the code</summary>

@@

<details>
<summary>Import data/click to see the code</summary>

@@

# Reults and discussion

@@

<details>
<summary>Some descriptive statistics/click to see the code</summary>
```{r warning=FALSE, message=FALSE,error=FALSE, echo=FALSE, results='hide'}

@@

```{r echo=F, eval=T, message=F , warning= FALSE, results='hide'}
IND_kable
```

```{r echo=F, eval=T, message=F , warning= FALSE, results='hide'}
# Portals by reach
reach <- dta %>%
  group_by(FROM) %>%
  summarise(reach = sum(REACH)) %>%
  arrange(desc(reach))

@@

@@

# Create the clickbait DataFrame
clickbait <- data.frame(
  number = c(1, 2, 3, 4, 5, 6, 7),
  text = c("Use of vague pronouns", "Uncertainty", "Reverse narrative style",
           "Emphasis on emotions", "Use of numbers", "Multiple combinations",
           "Not a clickbait headline")
)

@@

# Display the result
result %>%
  select(text, count, mean_reach, median_reach, min_reach, max_reach, total_reach) %>%
  kable(format = "html", 
        col.names = c("Clickbait Type", "Count", "Mean Reach", "Median Reach", 
                      "Min Reach", "Max Reach", "Total Reach"),
        caption = "Table 1: Prevalence and reach of clickbait headline characteristics in the analysed native ads (n=543)") %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed"), 
                full_width = F, position = "left")

@@

# Create the 'oprema' DataFrame
oprema <- data.frame(
  number = c(1, 2, 3, 4, 5, 6, 7, 8),
  text = c(
    "Photo content",
    "Video content",
    "Graphics or infographics",
    "Photo and video content",
    "Photo and graphics content",
    "Video and graphics content",
    "Photo, video, and graphics content",
    "Article lacks visual elements"
  )
)

The advertiser's logo, or elements of the advertiser's visual identity, were included in the visual content of the analysed native ads in 34.44% of cases, while in 356 out of 543 analysed articles, this was not the case, meaning they did not contain a visual link to the advertiser.

Regarding the content characteristics of native ads in this study, the types of sources or statements in the articles were also observed, as shown in Table 3. The ratio of ads using sources to those that do not is approximately similar, with the most common sources in the ads being individuals from the organization, i.e., the advertiser (19.71%). The second most common sources, with a prevalence of 10.31%, were those not directly connected to the product or service, while multiple sources were present in 7.55% of the ads, and in 6.81% of the ads, there was testimony or a statement from a person presented as a direct user of the product or service. Celebrities were also used as sources in native ads, with brand ambassadors’ statements used in 4.79% of cases, and influencers or celebrities were present in 3.5% of the analysed ads.

Table 3. Representation of different types of sources in the statements and reach (n=543)

```{r echo=F, eval=T, message=F , warning= FALSE}
# Create the 'izvori' DataFrame
izvori <- data.frame(
  number = c(1, 2, 3, 4, 5, 6, 7),
  text = c(
    "No source / statement",
    "Source from the organization / company",
    "Brand ambassador",
    "Influencer / celebrity",
    "Direct user of the product or service",
    "Multiple sources",
    "Source unrelated to the product or service"
  )
)

@@

# Display the result
result %>%
  select(text, count, mean_reach, median_reach, min_reach, max_reach, total_reach) %>%
  kable(format = "html", 
        col.names = c("Source Type", "Count", "Mean Reach", "Median Reach", 
                      "Min Reach", "Max Reach", "Total Reach"),
        caption = "Table 3. Representation of different types of sources in the statements and reach (n=543)") %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed"), 
                full_width = F, position = "left")

@@

```{r  echo=F, eval=T, message=F , warning= FALSE, results='hide'}

@@

```{r echo=F, eval=T, message=F , warning= FALSE, results='hide'}

@@

# Step 3: Create a Table Showing Distribution
# You can simply view the table
# industry_clickbait %>%
#   select(category, text, Count, Percent) %>%
#   kable(format = "html", 
#         col.names = c("Industry", "Clickbait Type", "Count", "Percentage"),
#         caption = "Distribution of Clickbait Types Across Industries") %>%
#   kable_styling(bootstrap_options = c("striped", "hover", "condensed"), 
#                 full_width = F, position = "left")
# Optional Step: Create a Heatmap for Visualization
ggplot(industry_clickbait, aes(x = category, y = text, fill = Percent)) +
  geom_tile() +
  scale_fill_gradient(low = "white", high = "blue") +
  labs(title = "Graph 1: Distribution of different clickbait types across various industries",
       x = "Industry",
       y = "Clickbait Type",
       fill = "Percentage") +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))
```

@@

@@

@@
